imputation_stickle

### 2023-05-01 R/stickle_imputation.Rmd
Add folders for R code and Data
Created two new folders.  R, for R code, and Data, for data.

```{r setup, include=FALSE}
library(mixgb)
library(mice)
library(tidyverse)
library(janitor)
library(missMethods)
library(ROCR)

@@

#Checking imputation accuracy/viability

M = 5
k = 5
stick_matrix <- matrix(NA, nrow=nrow(extant_stickle), ncol = M)
set.seed(12)
fold <- sample(1:k, size = nrow(extant_stickle), replace=TRUE)
for(i in 1:k){
extant_stickle_temp <- extant_stickle
extant_stickle_temp$gender[fold==i] <- NA
imputed_stick <- mice(extant_stickle_temp,m=M)
for(n in 1:M){

>>>>

```{r setup, include=FALSE}
library(mixgb)
library(mice)
library(tidyverse)
library(janitor)
library(missMethods)
library(ROCR)
```

@@

#Checking imputation accuracy/viability
M = 5
k = 5
stick_matrix <- matrix(NA, nrow=nrow(extant_stickle), ncol = M)
set.seed(12)
fold <- sample(1:k, size = nrow(extant_stickle), replace=TRUE)
for(i in 1:k){
extant_stickle_temp <- extant_stickle
extant_stickle_temp$gender[fold==i] <- NA
imputed_stick <- mice(extant_stickle_temp,m=M)
for(n in 1:M){
